The Prevalence of E-Mail Header Injections on the World Wide Web

### 2016-05-23 Background/php.tex

\begin{lstlisting}[language=PHP,caption={PHP program with e-mail
      header injection vulnerability.},label={code:phpemi}, float]
$from = $_REQUEST['email'];
$subject = 'Hello XYZ';
$message = 'We need you to reset your password';
$to = 'xyz@xyz.edu';

// example attack string to be 
// injected as the value for
// $_REQUEST['email'] => 
// 's@s.com\nCC:spc@spc.com'
$retValue = mail($to, $subject, $message, "From: $from");
// E-Mail gets sent to both 
// xyz@xyz.edu AND spc@spc.com
\end{lstlisting}

>>>>

\begin{lstlisting}[language=PHP,caption={PHP program with e-mail
      header injection vulnerability.},label={code:phpemi}, float]
$from = $_REQUEST['email'];
$subject = 'Hello XYZ';
$message = 'We need you to reset your password';
$to = 'xyz@example.com';

// example attack string to be 
// injected as the value for
// $_REQUEST['email'] => 
// 'abc@example.com\nCC:spc@example.com'
$retValue = mail($to, $subject, $message, "From: $from");
// E-Mail gets sent to both 
// xyz@example.com AND spc@example.com
\end{lstlisting}

### 2016-05-23 Background/ruby.tex

message = """
From: Sai <schand31@asu.edu>
Subject: SMTP e-mail test
To: #{email}

This is a test e-mail message.
"""
# construct a post request with email set to attack_string
# attack_string => sai@sai.com%0abcc:spc@spc.com%0aSubject:Hello
Net::SMTP.start('localhost', 1025) do |smtp|
smtp.send_message message, 'schand31@asu.edu',
'to@todomain.com'
end
# Headers get added, and Subject field changes to what we set.
end
\end{lstlisting}

>>>>

message = """
From: Sch <sch@example.com>
Subject: SMTP e-mail test
To: #{email}

This is a test e-mail message.
"""
# construct a post request with email set to attack_string
# attack_string => sai@example.com%0abcc:spc@example.com%0aSubject:Hello
Net::SMTP.start('localhost', 1025) do |smtp|
smtp.send_message message, 'sch@example.com',
'to@todomain.com'
end
# Headers get added, and Subject field changes to what we set.
end
\end{lstlisting}

### 2016-05-23 abstract.tex

	This paper presents a scalable mechanism to automatically detect \ehi vulnerabilities and uses this mechanism to quantify the prevalence of \ehi vulnerabilities on the web. Using a black-box testing approach, the system crawled \urls URLs identify web pages which contained form fields. \forms such forms were found by the system, of which \emailforms forms contained \email fields. We then test \fuzzed forms to see if they would send us an \email, and \recd forms set us an \email. Of these \malfuzzed forms were tested with \ehi payloads and, of these, we found \success vulnerable URLs across \domains domains. Then, to demonstrate that \ehi vulnerabilities are actively being exploited to create a spamming platform, we found \ipsblacklist IPs that were vulnerable on spaming blacklists. This work shows that \ehi vulnerabilities are widespread widespread and deserve future research attention.
\end{abstract}

>>>>

	This paper presents a scalable mechanism to automatically detect \ehi vulnerabilities and uses this mechanism to quantify the prevalence of \ehi vulnerabilities on the web. Using a black-box testing approach, the system crawled \urls URLs identify web pages which contained form fields. \forms such forms were found by the system, of which \emailforms forms contained \email fields. We then test \fuzzed forms to see if they would send us an \email, and \recd forms set us an \email. Of these \malfuzzed forms were tested with \ehi payloads and, of these, we found \success vulnerable URLs across \domains domains. Then, to demonstrate that \ehi vulnerabilities are actively being exploited to create a spamming platform, we found \ipsblacklist IPs that were vulnerable on spamming blacklists. This work shows that \ehi vulnerabilities are widespread widespread and deserve future research attention.
\end{abstract}
